\chapter{Packages}
\label{chap:packages}

The \texttt{gucthesis} is built upon the standard \LaTeX\
\texttt{report} class. All commands from the \texttt{report} class can
be used, with the two exceptions of \verb+\subsubsection+ and
\verb+\paragraph+. This is because there should only be three
levels of headings according to the guidelines~\cite{GUCMaster}.

\section{Packages Used by gucthesis}
\label{sec:packages}
\n{testing}
In addition to the \texttt{report} document class,
\texttt{gucthesis} makes direct use of the following packages
that must hence be present:
\begin{description}
	\item[geometry:] used for setting the sizes of the margins and
  	headers.
	\item[fontenc:] used with option \texttt{T1} for forcing the Cork font
  	encoding (necessary for the Charter font).
	\item[charter:] load Charter as the default font.
	\item[euler:] load the Euler math fonts.
	\item[babel:] to load language specific strings. Reasonable options
	  include \texttt{british}, \texttt{american}, \texttt{norsk},
	  \texttt{nynorsk} and \texttt{samin}.
\end{description}

\section{Other Relevant Packages}
\label{sec:otherpackages}

The author of a thesis might want to use a bunch of different packages
to those described in Section~\ref{sec:packages} in order to have all features needed for their document. 
In particular, it is advised to use the following:
\begin{description}
	\item[inputenc:] to allow \LaTeX\ to use more than 7-bit ASCII for its
	  input. Most often, the option \texttt{latin1} will do.
	\item[graphicx:] to include graphics.
	\item[hyperref:] this is a very nice package that makes cross links in
	  pdf documents. Use with option \texttt{dvips} or \texttt{pdftex}
	  in accordance with the driver that you use. Unfortunately, hyperref
	  is not completely bugfree\dots
\end{description}

We can use itemization lists
\begin{itemize}
	\item This is a test of itemize
	\item This is the second item
	\begin{itemize}
		\item even deeper in the lists
		\item this is a second sub item
		\begin{itemize}
			\item Is there no end to item depth
			\item This is definately the deepest
		\end{itemize}
	\end{itemize}
	\item ending the first list
\end{itemize}
